\pkg{partykit}: A Modular Toolkit for Recursive Partytioning in \proglang{R}

### 2014-09-12 pkg/partykit/inst/mloss/letter_mloss2.tex
correct title
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@611 255f4249-2263-4417-b1ea-8498779e27a7

my co-author Achim Zeileis and I would like to resubmit the manuscript
``\textbf{partykit}: An Open-Source Toolkit for Recursive Partytioning in R'' to the
Machine Learning Open-Source Software track of the Journal of Machine
Learning Research.

We would like to thank the referees for their constructive reviews and
action editor Cheng Soon Ong for overseeing the review process. While
preparing this resubmission, we took all issues discussed by the referees
into account and revised both the \emph{partykit} package and the four-page
description. A detailed description of our revision can be found in the
point to point reply.

>>>>

my co-author Achim Zeileis and I would like to resubmit the manuscript
``\textbf{partykit}: A Modular Toolkit for Recursive Partytioning in R'' to the
Machine Learning Open-Source Software track of the Journal of Machine
Learning Research.

We would like to thank the referees for their constructive reviews and
action editor Cheng Soon Ong for overseeing the review process. While
preparing this resubmission, we took all issues discussed by the referees
into account and revised both the \textbf{partykit} package and the four-page
description. A detailed description of our revision can be found in the
point to point reply.
